### 2020-12-02 05_Thesis/THESIS_LaTeX/Chapters/3.tex
final work done

Zhenan Bao et al. \cite{Liu2015a} investigated the effect of the polymer chemical structure (the effect of benzene rings) on the morphology, dimensions, composition, graphitization degree, crystallinity, and electrical conductivity of graphene nano-ribbons derived from four different types of electrospun polymers. The authors studied four polymers polystyrene (PS), poly(vinyl alcohol) (PVA), polyvinylphenol (PVP), and a phenolic resin known as Novolac. See Figure \ref{fig:zhenanBaoPolymers}. The authors created  electrospun polymer fibers out of the four selected polymers. PVP, Novolac and PVA have hydroxyl groups that can be functionalized with metal cations, while PS does not have such binding capability. On the other hand, PVP and Novolac have one benzene ring in each repeating unit, wheras PVA is mainly made out of sp3 carbon.

@@

Zhenan Bao et al. \cite{Liu2015a} found that higher sp2 carbon content (or more benzene rings) in the polymer chemical structure translates into higher graphitization degree and higher electrical conductivity in the final carbon structures. This finding can be use as a guide when choosing polymer precursors for the fabrication of carbon structures. Furthermore, the authors posit that polymers with functional groups are required for the creation of smooth and continuous fibers throw electrospinning. \cite{Liu2015a}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Selection of Candidate Spunable Polymer Solutions}
%high molecular weight, polymer-solution interaction (straight chains)
Given the conclusions from Zhenan Bao et al. \cite{Liu2015a} along with the extensive literature review and data analysis of Chapter \ref{Chapter:2}, the following polymer solutions were selected to be studied in this work. Polymer selection was based on the their high carbon content and presence of benzene rings. The purpose of the polymer selection is to focus the efforts to maximize the likelihood of polymers to yield carbon structures with high electrical conductivity and high graphitization degree; as testing every possible polymer-solvent system is not a practical way to carry on this research. Figure \ref{fig:selectedpolymers} lists the polymers that are going to be investigated. The selected polymers have been electrospun via far-field electrospinning for the fabrication of fibrous mats \cite{Fong1999, Min2013, Yousefi2019}, but no records of being spunable by NFES.

@@

Solutions at low concentrations do not allow polymer chains to entangle leading the viscoeslasticity od the solution dependent only on individual polymer chains. As the polymer concentration increases, the chains overlap and become entangled. The concentration at which the entanglement initially takes place is the critical concentration $c^*$. Concentrations above the critical concentration $c^*$ generate a fast increase in chain entanglement (Figure \ref{fig:criticalConcentrationEntanglement}). This rapid change in chain entanglement is translated into a fast increase in the viscoelasticity of the solution. Figure \ref{fig:concentrationViscosityPlotExplained} illustrates the relationship between polymer concentration and viscoelasticity. \cite{Burghelea2020, Gupta2005}

@@

Electrospinning of smooth, continuous fibers require a polymer concentration higher than the critical concentration. As shown in Figure \ref{fig:concentrationViscosityPlotExplained}, the critical concentration can be estimated from the change in slope. \cite{Burghelea2020, Gupta2005, Han2019} Therefore, in order to find the critical/spinnable concentrations of the candidate polymer-solvent solutions (poly(styrene-co-butadiene) in tetrahydrofuran, poly(9-vinyl carbazole) in chloroform, polyestyrene in tetrahydrofuran, and poly(styrene-co-a-methylstyrene) - See Figure \ref{fig:selectedpolymers}), it is necessary to build the appropriate viscosity vs. concentration plots as described in the following sections.

@@

Seven polymer-solvent combinations are to be tested. The Poly(Ethylene Oxide) and SU-8 2002 combination is what has been used in past work \cite{Cardenas2017, Flores2017}, and will be used as the control sample set. The selected polymer-solvent combinations are to investigate the ability of oxygenless polymers to be electrospun and then carbonized into vitreous carbon. Tables \ref{tab:PEOinSU8}, \ref{tab:PSBinNMP}, \ref{tab:PSBinTHFnDMF}, \ref{tab:PSMSinDMF}, \ref{tab:PSinTHF}, \ref{tab:PVKinCHL}, and \ref{tab:PVKinSU8} list the prepared polymer systems. Tetrabutylammonium tetrafluoroborate (TBF) was added to all solutions to increase the conductivity of the solution. SU-8 contains $71\%$ of cyclopentanone (CPO), which acts as the solvent (Figure \ref{fig:su8Components}) \cite{Microchem2012}.

@@

\begin{table}[!th]
\centering
\caption[Poly(Styrene-co-Butadiene) in Tetrahydrofuran and N,N-Dimethylformamide : Sample Preparation]{Poly(Styrene-co-Butadiene) in Tetrahydrofuran and N,N-Dimethylformamide : Sample Preparation}
\begin{tabular}{ccccc}
\hline
\textbf{Sample} & \multicolumn{4}{c}{\textbf{Weight Percent} $wt\%$} \\
\hline
{}          & \textbf{THF} & \textbf{DMF} & \textbf{PSB} & \textbf{TBF} \\
\textbf{18} & 70.875       & 23.625       &  5.00        & 0.50         \\
\textbf{19} & 69.000       & 23.000       &  7.50        & 0.50         \\
\textbf{20} & 67.125       & 22.375       & 10.00        & 0.50         \\
\textbf{21} & 65.250       & 21.750       & 12.50        & 0.50         \\
\textbf{22} & 63.375       & 21.125       & 15.00        & 0.50         \\
\textbf{23} & 59.625       & 19.875       & 20.00        & 0.50         \\
\textbf{24} & 55.875       & 18.625       & 25.00        & 0.50         \\
\hline
density $[\textrm{g} / \textrm{ml}]$
   & 0.888        & 0.950        & {}           & {}           \\
\hline
\end{tabular}
\label{tab:PSBinTHFnDMF}
\end{table}

@@

SU-8 2002 was obtained from MicroChem (Newton, MA, USA), while Tetrabutylammonium Tetrafluoroborate (TBF) of $99\%$ purity were, Poly(Ethylene Oxide) (PEO), Polystyrene (PS), Poly(Styrene-co-Butadiene) (PSB), Poly(Styrene-co-alpha-Methylstyrene) (PSMS), Poly(9-Vinylcarbazole) (PVK), Tetrahydrofuran (THF), 1-Methyl-2-Pyrrolidinone (NMP), N,N-Dimethylformamide (DMF), and Chloroform (CHL) were obtained from Sigma-Aldrich (Saint Louis, MI, USA). PEO has a viscosity-average molecular weight Mv of ~4,000,000, with less than 1000 ppm of Butylated Hydroxytoluene (BHT) as an inhibitor. PS has an average molecular weight Mw of ~192,000. PSB has a melt index of $6 \textrm{g} / 10 \textrm{min} (200^{\circ}C / 5 \textrm{kg})$, where the butadiene comprises 4 $wt\%$ PSMS has a melt viscosity of $10 \textrm{Pa} \cdot \textrm{s}$ at $161^{\circ}C$. PVK has an average molecular weight Mw of ~1,100,000 in powder form. THF is anhydrous and contained no inhibitor with $99.9\%$ purity. NMP is anhydrous with $99.5\%$ purity. DMF is anhydrous with $99.8\%$ purity. CHL has $99.5\%$ purity, a melting point of $-63^{\circ}C$, boiling point of $60.5^{\circ}C$, and a density of $1.492 \textrm{g} / \textrm{ml}$ at $25^{\circ}C$. CHL contains between 100 to 200 ppm amylenes as stabilizer. SU-8 is a high contrast, epoxy-based negative photoresist. All of the reactants were used as received.

Samples of 3 militers were prepared with the adecuate amounts of polymer, salt and solvent. Solutions were stired at $160 rpm$ for $2 hours$ at $60^{\circ}C$. Samples with higher polymer concentrations often required more stirring time to eliminate all polymer aggregates. All solutions were left undisturbed for $3 hours$ in 4 ml vials to eliminate bubbles from the solution.

\subsection{Rheological Characterization of polymer Solutions}
All of the rheological tests were performed in a rotational rheometer (Discovery Hybrid Rheometer DHR, TA Instruments) equipped with a cone-and-plate (CP) geometry (diameter of $60 mm$, angle of $0.9969^{\circ}$, and truncation of $23 \mu m$) in a steel Peltier plate (Figure \ref{fig:solventTrap}a). The experiments were conducted at $20^{\circ}C$ and $3 hours$ after polymer solution preparation. Flow curve (FC) tests were conducted to obtain viscosity curves in function of the shear rate. Analysis were performed at shear rate range from $10^{-3} \textrm{ 1} / \textrm{s}$ to $10^{4} \textrm{ 1} / \textrm{s}$. A solvent trap cover (Figure \ref{fig:solventTrap}f) and solvent trap geometry (Figure \ref{fig:solventTrap}a) were used to create a thermally stable vapor barrier, virtually eliminating any solvent loss during the rheological experiments and improving temperature uniformity. Distilled water was used to create a seal between the CP geometry and the solvent trap cover (Figure \ref{fig:solventTrap}e).

@@

Where: $\eta$ is the viscosity, $\dot{\gamma}$ the shear rate, $\eta_{\infty}$ the  infinite shear rate viscosity, $\eta_0$ the zero shear rate viscosity, $\kappa$ is the time constant, $n$ the Power Law index, $a$ the width of the transition region between the zero shear viscosity and the Power Law region. The model was fitted to the rheologial data to estimate $\eta_0$. Then, $\eta_0$ values are used to create diagrams that describe the effect of polymer concentration on the solution viscosity, as described in Figure \ref{fig:concentrationViscosityPlotExplained}. The critical concentrations are calculated from the change in slope in the zero-shear viscosity to concentration relationship as depicted in Figure \ref{fig:criticalConcentrationCalculation} for the PEO in SU-8 solutions. Appendix \ref{Appendix_CriticalConcentrations} contains the diagrams of the other polymer-solvent systems.

@@

Table \ref{tab:calculatedSpinnableConcentrations} summarizes the calculated critical concentrations for each system. In general, the critical concentration $c^*$ has proportional relationship with the polymer molecular weight, as a polymer's molecular weight greatly influences the solution viscosity. First, the structure of the polymer chain has an effect on its solubility as the intermolecular interactions between long molecules are stronger and the solvent molecules take longer to diffuse within the polymer aggregates. \cite{Ramakrishna2005, Floreshernandez2020} Second, the viscosity of a polymer solution will be smaller when a polymer of low molecular weight is dissolved than a solution of the same polymer but of a higher molecular weight. \cite{Ramakrishna2005} The molecular weight of the polymer describes the length of the polymer chain, which has an effect on the viscosity of the solution. Since the polymer length defines the amount of entanglement of the polymer chains in the solvent, a lower molecular weight shall be compensated by higher concentrations to reach the desired viscosity.

>>>>

Zhenan Bao et al. \cite{Liu2015a} investigated the effect of the polymer chemical structure (the effect of benzene rings) on the morphology, dimensions, composition, graphitization degree, crystallinity, and electrical conductivity of graphene nano-ribbons derived from four different types of electrospun polymers as templating agents. The authors studied four polymers polystyrene (PS), poly(vinyl alcohol) (PVA), polyvinylphenol (PVP), and a phenolic resin known as Novolac. See Figure \ref{fig:zhenanBaoPolymers}. The authors created  electrospun polymer fibers out of the four selected polymers. PVP, Novolac and PVA have hydroxyl groups that can be functionalized with metal cations, while PS does not have such binding capability. On the other hand, PVP and Novolac have one benzene ring in each repeating unit, wheras PVA is mainly made out of sp3-hybridized carbon.

@@

Zhenan Bao et al. \cite{Liu2015a} found that higher sp2 carbon content (or more benzene rings) in the polymer chemical structure translates into higher graphitization degree and higher electrical conductivity in the final carbon structures. This finding can be use as a guide when choosing polymer precursors for the fabrication of carbon structures. Furthermore, the authors posit that polymers with functional OH groups are required for the creation of smooth and continuous fibers throw electrospinning. \cite{Liu2015a}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Selection of Candidate Spunable Polymer Solutions}
%high molecular weight, polymer-solution interaction (straight chains)
Given the conclusions from Zhenan Bao et al. \cite{Liu2015a} along with the extensive literature review and data analysis of Chapter \ref{Chapter:2}, the following polymer-solvent combinations were selected to be studied in this work. Polymer selection was based on the their high carbon content and presence of benzene rings. The purpose of the polymer selection is to focus the efforts to maximize the likelihood of polymers to yield carbon structures with high electrical conductivity and a higher degree of graphitization as compared to the previously used SU-8/PEO combination in cyclopentanone; as testing every possible polymer-solvent system is not a practical way to carry on this research. Figure \ref{fig:selectedpolymers} lists the polymers that are going to be investigated along with their proposed solvents. The selected polymers have been electrospun via far-field electrospinning for the fabrication of fibrous mats \cite{Fong1999, Min2013, Yousefi2019}, but no records of being spunable by NFES.

@@

Solutions at low concentrations do not allow polymer chains to entangle, leading the viscoeslasticity of the solution dependent only on the interaction of individual polymer chains. As the polymer concentration increases, the chains overlap and becomes entangled. The concentration at which the entanglement initially takes place is the critical concentration $c^*$. Concentrations above the critical concentration $c^*$ generate a fast increase in chain entanglement (Figure \ref{fig:criticalConcentrationEntanglement}). This rapid change in chain entanglement is translated into a fast increase in the viscosity of the solution. Figure \ref{fig:concentrationViscosityPlotExplained} illustrates the relationship between polymer concentration and viscoelasticity. \cite{Burghelea2020, Gupta2005}

@@

Electrospinning of smooth, continuous fibers require a polymer concentration equal or higher than the critical concentration. As shown in Figure \ref{fig:concentrationViscosityPlotExplained}, the critical concentration can be estimated from the change in slope of the log-viscosity to log-concentration curve. \cite{Burghelea2020, Gupta2005, Han2019} Therefore, in order to find the critical/spinnable concentrations of the candidate polymer-solvent solutions (poly(styrene-co-butadiene) in tetrahydrofuran, poly(9-vinyl carbazole) in chloroform, polyestyrene in tetrahydrofuran, and poly(styrene-co-a-methylstyrene) - See Figure \ref{fig:selectedpolymers}), it is necessary to build the appropriate viscosity vs. concentration plots as described in the following sections.

@@

Seven polymer-solvent combinations are to be tested. The Poly(Ethylene Oxide) and SU-8 2002 combination is what has been used in previous work \cite{Cardenas2017, Flores2017}, and will be used as the control sample set. The selected polymer-solvent combinations were selected to investigate the ability of oxygenless polymers to be electrospun and then carbonized into vitreous carbon. Tables \ref{tab:PEOinSU8}, \ref{tab:PSBinNMP}, \ref{tab:PSBinTHFnDMF}, \ref{tab:PSMSinDMF}, \ref{tab:PSinTHF}, \ref{tab:PVKinCHL}, and \ref{tab:PVKinSU8} list the prepared polymer systems. Tetrabutylammonium tetrafluoroborate (TBF) was added to all solutions to increase the conductivity of the solution. SU-8 contains $71\%$ of cyclopentanone (CPO), which acts as the solvent (Figure \ref{fig:su8Components}) \cite{Microchem2012}.

@@

\begin{table}[!th]
\centering
\caption[Poly(Styrene-co-Butadiene) in Tetrahydrofuran and N,N-Dimethylformamide : Sample Preparation]{Poly(Styrene-co-Butadiene) in Tetrahydrofuran and N,N-Dimethylformamide : Sample Preparation}
\begin{tabular}{ccccc}
\hline
\textbf{Sample} & \multicolumn{4}{c}{\textbf{Weight Percent} $wt\%$} \\
\hline
{}          & \textbf{THF} & \textbf{DMF} & \textbf{PSB} & \textbf{TBF} \\
\textbf{18} & 70.87        & 23.63        &  5.00        & 0.50         \\
\textbf{19} & 69.00        & 23.00        &  7.50        & 0.50         \\
\textbf{20} & 67.12        & 22.38        & 10.00        & 0.50         \\
\textbf{21} & 65.25        & 21.75        & 12.50        & 0.50         \\
\textbf{22} & 63.37        & 21.13        & 15.00        & 0.50         \\
\textbf{23} & 59.62        & 19.88        & 20.00        & 0.50         \\
\textbf{24} & 55.87        & 18.63        & 25.00        & 0.50         \\
\hline
density $[\textrm{g} / \textrm{ml}]$
   & 0.888        & 0.950        & {}           & {}           \\
\hline
\end{tabular}
\label{tab:PSBinTHFnDMF}
\end{table}

@@

SU-8 2002 was obtained from MicroChem (Newton, MA, USA), while Tetrabutylammonium Tetrafluoroborate (TBF) of $99\%$ purity were, Poly(Ethylene Oxide) (PEO), Polystyrene (PS), Poly(Styrene-co-Butadiene) (PSB), Poly(Styrene-co-alpha-Methylstyrene) (PSMS), Poly(9-Vinylcarbazole) (PVK), Tetrahydrofuran (THF), 1-Methyl-2-Pyrrolidinone (NMP), N,N-Dimethylformamide (DMF), and Chloroform (CHL) were obtained from Sigma-Aldrich (Saint Louis, MI, USA). PEO has a viscosity-average molecular weight Mw of ~4,000,000, with less than 1000 ppm of Butylated Hydroxytoluene (BHT) as an inhibitor. PS has an average molecular weight Mw of ~192,000. PSB has a melt index of $6 \textrm{g} / 10 \textrm{min} (200^{\circ}C / 5 \textrm{kg})$, where the butadiene comprises 4 $wt\%$ PSMS has a melt viscosity of $10 \textrm{Pa} \cdot \textrm{s}$ at $161^{\circ}C$. PVK has an average molecular weight Mw of ~1,100,000 in powder form. THF is anhydrous and contained no inhibitor with $99.9\%$ purity. NMP is anhydrous with $99.5\%$ purity. DMF is anhydrous with $99.8\%$ purity. CHL has $99.5\%$ purity, a melting point of $-63^{\circ}C$, boiling point of $60.5^{\circ}C$, and a density of $1.492 \textrm{g} / \textrm{ml}$ at $25^{\circ}C$. CHL contains between 100 to 200 ppm amylenes as stabilizer. SU-8 is a high contrast, epoxy-based negative photoresist. All of the reactants were used as received.

Samples of 3 milliliters were prepared with the adecuate amounts of polymer, salt and solvent. Solutions were stired at $160 \textrm{ rpm}$ for $2 \textrm{ hours}$ at $60^{\circ}C$. Samples with higher polymer concentrations often required more stirring time to eliminate all polymer aggregates. All solutions were left undisturbed for $3 \textrm{ hours}$ in $4 \textrm{ ml}$ vials to eliminate bubbles from the solution.

\subsection{Rheological Characterization of polymer Solutions}
All of the rheological tests were performed in a rotational rheometer (Discovery Hybrid Rheometer DHR, TA Instruments) equipped with a cone-and-plate (CP) geometry (diameter of $60 \textrm{ mm}$, angle of $0.9969^{\circ}$, and truncation of $23 \textrm{ } \mu \textrm{m}$) in a steel Peltier plate (Figure \ref{fig:solventTrap}a). The experiments were conducted at $20^{\circ}C$ and $3 \textrm{ hours}$ after polymer solution preparation. Flow curve (FC) tests were conducted to obtain viscosity curves as a function of the shear rate. Analysis were performed at shear rate range from $10^{-3} \textrm{ 1} / \textrm{s}$ to $10^{4} \textrm{ 1} / \textrm{s}$. A solvent trap cover (Figure \ref{fig:solventTrap}f) and solvent trap geometry (Figure \ref{fig:solventTrap}a) were used to create a thermally stable vapor barrier, virtually eliminating any solvent loss during the rheological experiments and improving temperature uniformity. Distilled water was used to create a seal between the CP geometry and the solvent trap cover (Figure \ref{fig:solventTrap}e).

@@

Where: $\eta$ is the viscosity, $\dot{\gamma}$ the shear rate, $\eta_{\infty}$ the  infinite shear rate viscosity, $\eta_0$ the zero shear rate viscosity, $\kappa$ is the time constant, $n$ the Power Law index, $a$ the width of the transition region between the zero shear viscosity and the Power Law region. The features of the flow curves shown in Appendix \ref{Appendix_flowCurves} can be modeled using the Carreau-Yasuda model, with the benefits that it is possible to describe the shape and curvature of a flow curve through six fitting parameters and to predict behavior at unmeasured shear rates. The Carreau-Yasuda model is most applicable model due to the range of the measured data. Unlike the Sisko and Williamson models, the Carreau-Yassuda model considers both the infinite- and zero-shear rate viscosities.

The Carreau-Yasuda model was fitted to the rheologial data to estimate $\eta_0$. Then, $\eta_0$ values are used to create diagrams that describe the effect of polymer concentration on the solution viscosity, as described in Figure \ref{fig:concentrationViscosityPlotExplained}. The critical concentrations are calculated from the change in slope in the zero-shear viscosity to concentration relationship as depicted in Figure \ref{fig:criticalConcentrationCalculation} for the PEO in SU-8 solutions. Appendix \ref{Appendix_CriticalConcentrations} contains the diagrams of the other polymer-solvent systems.

@@

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/ALLcriticalConcentrationCalculation.png}
\decoRule
\caption[Estimation of the Critical Concentration of the Candidate Polymer-Solvent Combinations]{Estimation of the Critical Concentration of the Candidate Polymer-Solvent Combinations. Individual plots are available in Appendix \ref{Appendix_CriticalConcentrations}}
\label{fig:ALLcriticalConcentrationCalculation}
\end{figure}

Table \ref{tab:calculatedSpinnableConcentrations} was built from Figure \ref{fig:ALLcriticalConcentrationCalculation}, and summarizes the calculated critical concentrations for each system. In general, the critical concentration $c^*$ has a directly proportional relationship with the polymer molecular weight, as a polymer's molecular weight greatly influences the solution viscosity. First, the structure of the polymer chain has an effect on its solubility as the inter-molecular interactions between long molecules are stronger and the solvent molecules take longer to diffuse within the polymer aggregates. \cite{Ramakrishna2005, Floreshernandez2020} Second, the viscosity of a polymer solution will be smaller when a polymer of low molecular weight is dissolved than a solution of the same polymer but of a higher molecular weight. \cite{Ramakrishna2005} The molecular weight of the polymer describes the length of the polymer chain, which has an effect on the viscosity of the solution. Since the polymer length defines the amount of entanglement of the polymer chains in the solvent, a lower molecular weight shall be compensated by higher concentrations to reach the desired viscosity, see Figure \ref{fig:criticalConcentrationViscoAndMolWeight}.

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/criticalConcentrationViscoAndMolWeight.png}
\decoRule
\caption{Relationship between the critical concentrations, molecular weights, and zero-shear viscosities of the selected polymer solutions.}
\label{fig:criticalConcentrationViscoAndMolWeight}
\end{figure}

### 2020-12-02 05_Thesis/THESIS_LaTeX/Chapters/4.tex
defense update
final work done

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{}

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------
\section{}

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------
\section{Fabrication and Characterization of Legacy SU-8 carbon fibers}

\section{\emph{conclude with fibre morphology before and after pyrolysis. determine best pyrolysis process}}
%Were the selected candidates electrospunable?
%Fiber morphology
%Yield rate
%Carbon content
%Conductivity
%Fiber morphology

>>>>

The fabrication and characterization of polymeric fibers is addressed in this chapter as the last screening procedure to select the PEO/SU-8 replacement. The PEO/SU-8 replacement is to produce microscopic polymer fibers with potential for the fabrication of carbon nano-wires. This chapter reports PEO, PS, PSB, and PVK micro-fibers fabricated by low-voltage near-field electrospinning. The fabrication process is carried on to study the influence of applied voltage on the fiber diameter. The materials and sample preparation for the LV-NFES process are the same as those used in the rheological analyses in Chapter \ref{Chapter:3}.

\section{Near-Field Electrospinning Setup}

\begin{figure}[!th]
\centering
\includegraphics[scale=0.50]{./Figures/NFESsetup.png}
\decoRule
\caption[NFES experimental setup]{NFES experimental setup. Adapted from \cite{Floreshernandez2020}}
\label{fig:NFESsetup}
\end{figure}

The near-field apparatus (Figure \ref{fig:NFESsetup}) is comprised by a high voltage supply (HVS448 3000 V, LabSmith, Livermore, CA, USA), a three-axis stage, syringe pump (Pump 11 Elite, Harvard Apparatus, Cambridge, MA, USA). Samples were prepared as per the rheology measurements in Chapter \ref{Chapter:3}. Experiments were conducted with 1 milliliter slip-tip insulin syringes with 21 gauge precision tips (Nordson Engineered Fluid Dispensing, Westlake, OH, USA). The power supply and 3-axis stage are controlled through a desktop computer, while the syringe pump is controlled manually. Fiber depositions were placed on a $\textrm{Si}-\textrm{SiO}_2$ wafer. The voltage between the nozzle tip and the collector was varied between $200 [\textrm{V}]$ and $600 [\textrm{V}]$ in increments of $100 [\textrm{V}]$, keeping a constant current of $10 \textrm{ } \mu \textrm{A}$. For applied voltages under $400 [\textrm{V}]$, the electric field was not strong enough to overcome the surface tension of the polymer solution and initiate the jet. To enable the fiber deposition at low voltages, the polymer jet was manually initialized by breaking the surface tension with a sharp glass tip. The working distance $L$ and stage velocity was set at a constant values for all the experiments at $0.5 mm$ and $10 mm/s$ respectively. The syringe pump was set at a steady flow rate of $0.04 \mu \textrm{L} / \textrm{min}$.

\begin{figure}[!th]
\centering
\includegraphics[scale=0.50]{./Figures/microscope.png}
\decoRule
\caption{Correct, Seiwa Optical - Optical Microscope}
\label{fig:microscope}
\end{figure}

The applied voltage range was set in a range between $200 [\textrm{V}]$ and $600 [\textrm{V}]$, since within that range fibers were able to electrospun into continuous and straight fibers. As shown in Figure \ref{fig:lowVoltageHighVoltage}, PEO/SU-8 fibers are produced with a meander morphology when the applied voltage is around $900 [\textrm{V}]$. Under $600 [\textrm{V}]$, straight and aligned fibers were fabricated and characterized.

The calculated critical concentrations in Chapter \ref{Chapter:3} (Table \ref{tab:calculatedSpinnableConcentrations}) are used for the fabrication of polymeric fibers. One set of experiments was conducted for each polymer-solvent system to study the effect of applied voltage on fiber diameter. The morphology of the fibers was characterized with an optical microscope (Correct, Seiwa Optical, Dallas, TX, USA, Figure \ref{fig:microscope}). Each sample was measured at 30+ points within the microscope field of view (Appendix \ref{Appendix_MicroscopyChar}).

\begin{figure}[!th]
\centering
\includegraphics[scale=0.40]{./Figures/lowVoltageHighVoltage.png}
\decoRule
\caption{Effect of applied voltage in fiber morphology}
\label{fig:lowVoltageHighVoltage}
\end{figure}

\section{Results}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/boxplotsFiberDiameter.png}
\decoRule
\caption[Diameter of fibres for all the experiments]{Diameter of fibres for all the experiments with varing applied voltage $\Phi_0$. Appendix \ref{Appendix_FiberDiameters}}
\label{fig:boxplotsFiberDiameter}
\end{figure}

Figure \ref{fig:boxplotsFiberDiameter} shows a dependence of fiber diameter as a function of the applied voltage and confirms what was already noticed in the correlation matrix and the adimensional analysis in Chapter \ref{Chapter:2}, as lower voltages yield fibers with thinner diameters. This results verify the electro-spinnability of oxygen-less polymers by NFES into fibers of $1 \mu m$ to $5 \mu m$ in diameter. PS presented complications during the NFES process as fibers of this polymer do not adhere onto the substrate making them prone to fracture or substrate abandonment, specially when printing fibers of thin diameters. To ease this complication the working distance $L$ can be reduced to let the fibers dry on the surface and prevent complete solidification while traveling the distance $L$. The increase in applied voltage can also help with this problem as more material is pulled out of the dispensing needle, however this two fixes will translate into thicker fibers.

The effect of applied voltage on fiber diameter can be contributed to the effect of the electric field on the surface tension of the polymer solution drop. Bateni and coworkers \cite{Bateni2005} have shown that surface tension increases with increasing applied voltage. Bateni also states that the effect of an electric field is stronger on alcohols with higher molecular weights \cite{Bateni2005}. Bateni's findings agree with Zhenan Bao's statements regarding polymers with OH functional groups are more easily electrospun than those without functional groups \cite{Liu2015a, Bateni2005}. Since the tested polymers are of different molecular weights, the effect of applied voltage is more significant in the PEO/SU-8 formulation as PEO has the highest molecular weight. On the other hand, the PSB in THF and DMF solution was the least affected by changes in applied voltage as PSB has the smallest molecular weight. Disregarding the molecular weight, the PS formulation has higher variation in fiber diameter. This outcome can be explained by the poor adhesion of the fibers to the substrate, as explained above. The effect of the applied voltage between the two PVK samples present some differences. The PVK in CHL solution has a stronger reaction to the electric field than the PVK in SU-8 formulation. This difference can be attributed to the fact that SU-8 is comprised by a series of monomers of low molecular weight.

The PVK and CHL system was the one that behaved with more similarity as the control sample of SU-8 and PEO. Uniform, $700 \textrm{ nm}$ diameter fibers were achieved with PVK and CHL at the lowest voltage setting ($200 \textrm{ V}$). Given the similarities with the control sample, PVK was choosen to replace the PEO to increase the spinnability of SU8. Therefore, the PVK in SU-8 system was tested in the same conditions as the previous experiments. Both polymers (PEO and PVK) in SU-8 yield parallel results in fiber morphology and in electrospinning preformanc. However, at high voltages, the PVK solution produced thinner fibers than those produced by the PEO solution. Moreover, as PVK does not contain any additional oxygen content in its structure, adding PVK can be a better alternative to electrospun SU-8 based fibers intended for carbonization as thinner fibers will have better opportunities to survive the pyrolysis process without breaking.

On the other hand, the polymer-solvent systems comprised by Poly(Styrene-co-Butadiene) (PSB) in 1-Methyl-2-Pyrrolidinone (NMP) and Poly(Styrene-co-alpha-Methylstyrene) (PSMS) in N,N-Dimethylformamide (DMF) were unable to yield fibers. In the case of the PSB/NMP solutions, a hard shell was formed around the polymer drop at the tip of the nozzle preventing the jet to initiate, which causes clogging. Seems that rapid volatilization of NMP is not the case as PSB was successfully electrospun with more volatile solvents (THF and DMF). Notice that vapor pressure of NMP is around $39 \textrm{Pa}$ at $25^{\circ} C$, THF and DMF have vapor pressures of about $19.3 \textrm{kPa}$ at $20^{\circ} C$ and $0.49 \textrm{kPa}$ at $25^{\circ} C$ respectively. \cite{ICSCs} On the other hand, PSMS in DMF was not able to produce fibers as the jet was not initiated. After noticing that que calculated critical concentration $c^*$ is not spinnable the solutions of 10 and 15 $wt\%$ were also tested in the NFES apparatus with no success. The cause of the non-spinnable nature of PSMS can be laid on the fact that PSMS pellets were brittle and capable of making fine PSMS dust with ease, unlike PS and PSB pellets which have an elastic behavior.
